The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2022-01-29 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd
Addressing more concerns from reviewer 1

Moving on to the main focus of the study, comparing 2020 to 2017-2019.
Figure \@ref(fig:Fig2) shows the histograms of the home (green) and
away scoring (red) for 2020 vs. 2017-2019. All histograms are
fairly bell shaped, which is important for statistical tests
designed for normally distribute data. There appears to be little
difference between the 2020 and 2017-2019 for home scoring, but for
away scoring, a noticeable shift to the right in 2020 is observed
compared with that in 2017-2019.

@@

```{r table, echo = FALSE}
knitr::kable(resultsfinal, caption = 'The results from the 9 tests', align = "cccccc", booktabs = TRUE)
```

>>>>

Moving on to the main focus of the study, comparing 2020 to 2017-2019.
Figure \@ref(fig:Fig2) shows the histograms of the home (green) and
away scoring (red) for 2020 vs. 2017-2019. All histograms are
fairly bell shaped, which is important for statistical tests
designed for normally distribute data. There appears to be little
difference between the 2020 and 2017-2019 for home scoring, but for
away scoring, a more pronounced shift to the right in 2020 is observed
compared with that in 2017-2019.

@@

```{r table, echo = FALSE}
knitr::kable(resultsfinal, caption = 'The results from the 9 tests', align = "cccccc", booktabs = TRUE)
```
Note: Home and Away scoring totals are divided by 100
